Paper without a name

### 2014-05-09 Article.tex
Include SVG
add pdf_tex files
Dynamic generation of pdf_tex files
Stuff.

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{url}

@@

\title{Paper without a name}
\author{A. Auvolat \and A. Fromherz \and N. Jeannerod}
\date{June 01, 2014}
\maketitle

@@

In this contribution, we investigate the problem of "SwitchBoxes".  The goal is,
given $n$ wires, to generate all the permutations of these wires by using
"boxes", that swap two wires. We tried to minimize the number of boxes that were
necessary.  We introduce a conjecture that puts our problem in relation with
binary insertion sort.  We successfully used a heavily optimized algorithm to
prove this conjecture for small values of $n$.

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

\newcommand{\includesvg}[1]{%
  \input{#1.pdf_tex}%
}

\graphicspath{{svg/}}

@@

\title{ Paper without a name }
\author{A. Auvolat \and A. Fromherz \and N. Jeannerod }
\date{June 01, 2014}
\maketitle

@@

In this contribution, we investigate the problem of ``SwitchBoxes''.  The goal is,
given $n$ wires, to generate all the permutations of these wires by using
``boxes'', that swap two wires. We tried to minimize the number of boxes that were
necessary.  We introduce a conjecture that puts our problem in relation with
binary insertion sort.  We successfully used a heavily optimized algorithm to
prove this conjecture for small values of $n$.

@@

\begin{figure}
 \centering
 \begin{minipage}{.5\textwidth}
 	\centering
	 \def\svgwidth{0.2\textwidth}
	 \includesvg{svg/2wires_box}
	 \caption{Trivial solution for 2 wires}
 \end{minipage}%
 \begin{minipage}{.5\textwidth}
 	\centering
	 \def\svgwidth{0.5\textwidth}
	 \includesvg{svg/4wires_box}
	 \caption{Simple non-optimal solution for 4 wires}
 \end{minipage}
\end{figure}

\begin{figure}
	\centering
	\def\svgwidth{0.6\textwidth}
	\includesvg{svg/8wires_box}
	\caption{Simple non-optimal solution for 8 wires}
\end{figure}
